An Overview of the Current State of Test-First vs. Test-Last Debate

### 2013-11-24 Paper_Draft.tex
should be ready to go.

>>>>

Last, is a 2007 opinion study by Janzen \cite{Janzen:2007}.  In this opinion study, Janzen polled participants from six experiments to determine whether they preferred testing with test-first methods or test-last methods.  Five of these experiments were conducted on students at the University of Kansas while one of the experiments was conducted on professional programmers from a Fortune 500 company.  Each participant was asked six questions where they had to choose between test-first and test-last testing.  The questions were:

\begin{itemize}
\item which approach they would choose in the future (\textbf{Choice})
\item which approach was the best for the project(s) they
completed (\textbf{BestApproach})
\item which approach would cause them to more thoroughly
test a program (\textbf{ThoroughTesting})
\item which approach produces a correct solution in less
time (\textbf{Correct})
\item which approach produces code that is simpler, more
reusable, and more maintainable (\textbf{Simpler})
\item which approach produces code with fewer defects

(\textbf{FewerDefects})
\end{itemize}

The results of the study are shown in figure 1.  The results were divided between a beginner group (students within their first few code classes) and a mature group (students nearing graduation and professionals).  In the results section Janzen concluded that beginner coding students have a preference toward test-last testing while more mature coding students and industry professionals show a preference toward test-first testing.
